Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
the converse might not be true, if we don't consider all variable

Since all neurons are assumed to be connected to at least one neuron,
we thus have by definition $X_i \not\perp X_j$. However,  two random
variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
once we observe a third variables $C$ ($A \perp B | C$).
The conditioning over all other random variables $X^{-i,j}$ is thus necessary
to avoid predicting an edge when two neurons are not directly connected.

>>>>

Since all neurons are assumed to be connected to at least one neuron,
we thus have by definition $X_i \not\perp X_j$. However,  two random
variables $A$ and $B$ might be dependent taken alone ($A \not\perp B$), but not
once we observe the set  $C$ of all other variables ($A \perp B | C$).
The conditioning over all other random variables $X^{-i,j}$ is thus necessary
to avoid predicting an edge when two neurons are not directly connected.
